Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-31 tex/comments/3-nat-comments.tex
Addressed Miles comments on conjectures, added bibtex entries

 Due to the argument present in Theorem \ref{Irreducibility Theorem}, sign subrepresentations provide a surprisingly strong characterization of some $M_{2n + r}^r$ as follows.
 \begin{proposition}\label{Preimage of K}
 	{\color{red!80!green}This proposition can be strengthened, right? Like we just need a sequence of $n-n'$ actions such that no two of them are closer than two positions apart, right?}
 	Fix some $M := M_{2n + r}^r$.
 	Suppose there is some natural number $n'$ with $n' \leq n$ such that $K_{2n' + r}^r \neq 0$.
 	Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
 	\[
 	\pi := \begin{cases}
 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n,'\\
 	\id{M} & \text{if } n = n',
 	\end{cases}
 	\]
  where $\id M$ is the identity map on $M_{2n + r}^r$.
  Then, $\pi^{-1}(K_{2n' + r}^r)$ contains any proper subrepresentations of $M_{2n + r}^r$.
 \end{proposition}
 \begin{proof}
 	It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
 	then, any subrepresentation containing $w$ also contains all of $M$, implying the proposition.

 	In fact, since $\pi(w) \notin K$, there is some $(1 + T_i) \in \SH$ such that $(1 + T_i)\pi(w) \neq 0$.
 	Note that $e > (n'-1) + r + 1$, so $M_{2(n-1) + r}^r$ is irreducible;
 	then, we may use diagram \eqref{Irreducibility commutative diagram} and an analogous argument to Theorem \ref{Irreducibility Theorem} to argue that $(1 + T_i)\pi(w)$ is cyclic, and hence $w$ is cyclic.
 \end{proof}
 \begin{corollary}\label{n+r+1 composition series}
 	Suppose $e = n + r + 1$.
 	Then $M_{2n + r}^r$ has a composition series given by
 	\[
 	0 \subset K \subset M.
 	\]
 \end{corollary}

 This is suggestive;
 the preimage $\pi^{-1}(K)$ may play a key role in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
 The following section poses several conjectures involving this structure.

 \subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
 If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Proposition \ref{Preimage of K}.
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[Appendix~B]{Mathas-book};
 this is give heuristic support in Appendix \ref{Empirics Section}.
 This motivates our first conjecture:
 \begin{conjecture}\label{Preimage subrepresentation}
   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M$.
 \end{conjecture}
 {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}
 This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
 In general, this is surprising;
 $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.

@@

 These conjectures would characterize much of the structure of $M_{2n + r}^r$.
 We will pose a final conjecture as follows.
 \begin{conjecture}
 	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 \end{conjecture}
 The support for this includes {\color{magenta} FILL THIS IN.}

>>>>

 Due to the argument present in Theorem \ref{Irreducibility Theorem}, sign subrepresentations provide a surprisingly strong characterization of some $M_{2n + r}^r$ as follows.
 \begin{proposition}\label{Preimage of K}
 	Fix some $M := M_{2n + r}^r$.
 	Suppose there is some natural number $n'$ with $n' \leq n$ such that $K_{2n' + r}^r \neq 0$.
 	Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
 	\[
 	\pi := \begin{cases}
 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n',\\
 	\id{M} & \text{if } n = n',
 	\end{cases}
 	\]
  where $\id M$ is the identity map on $M_{2n + r}^r$.
  Then, $\pi^{-1}(K_{2n' + r}^r)$ contains any proper subrepresentations of $M_{2n + r}^r$.
 \end{proposition}
 \begin{proof}
   Set $M := M_{2n + r}$ and $K := K_{2n' + r}^r$.
  It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
 	then, any subrepresentation containing $w$ also contains all of $M$, implying the proposition.

 	In fact, since $\pi(w) \notin K$, there is some $(1 + T_i) \in \SH$ such that $(1 + T_i)\pi(w) \neq 0$.
 	Note that $e > (n'-1) + r + 1$, so $M_{2(n-1) + r}^r$ is irreducible;
 	then, we may use diagram \eqref{Irreducibility commutative diagram} and an analogous argument to Theorem \ref{Irreducibility Theorem} to argue that $(1 + T_i)\pi(w)$ is cyclic, and hence $w$ is cyclic.
 \end{proof}
 \begin{corollary}\label{n+r+1 composition series}
 	Suppose $e = n + r + 1$.
 	Then $M_{2n + r}^r$ has a composition series given by
 	\[
    0 \subset K_{2n + r}^r \subset M_{2n + r}^r.
 	\]
 \end{corollary}

 \begin{remark}
   In the case $n < n'$, we may replace $\pi$ with a product of $n-n'$ elements $(1 + T_{z_1})\cdots(1 + T_{z_{n-n'}}) \in \SH$ such that $\abs{z_i - z_j} \geq 2$ for each $1 \leq i < j \leq n-n'$.
   Then, an analogous statement to Proposition \ref{Preimage of K} follows from an analogous proof.
 \end{remark}

 Proposition \ref{Preimage of K} and Corollary \ref{n+r+1 composition series} are suggestive;
 the preimage $\pi^{-1}(K)$ may play a key role in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
 The following section poses several conjectures involving this structure.

 \subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
 If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Proposition \ref{Preimage of K}.
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[Appendix~B]{Mathas-book};
 this is give heuristic support in Appendix \ref{Empirics Section}.
 This motivates our first conjecture:
 \begin{conjecture}\label{Preimage subrepresentation}
   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M$.
 \end{conjecture}
 This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
 In general, this is surprising;
 $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.

  \begin{remark}
    As a corollary to \ref{Preimage subrepresentation}, the quotient $M_{2n + r}^r / \pi^{-1}(K_{2n' + r}^r)$ is irreducible \cite[Thm.~10.4]{Dummit}.
  \end{remark}

@@

 These conjectures would characterize much of the structure of $M_{2n + r}^r$.
 We will pose a final conjecture as follows.
 \begin{conjecture}\label{Final conjecture}
 	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 \end{conjecture}
 The support for this includes the special case $e > n+r+1$ case proven in Theorem \ref{Correspondence Theorem}, as well as the previous contents of this section.
 Further, note that the basis of $M_{2n + r}^r$ is defined analogously for all $e$;
 it is well-known that a basis for $S^\lambda$ is indexed by the standard young tableaux of $\lambda$, which is also independent of $e$ \cite[Prop.~3.22]{Mathas-book}.
 Hence Theorem \ref{Correspondence Theorem} implies that $M_{2n + r}^r$ and $S^{(n+r,n)}$ have the same dimension. 
  These facts give heuristic support for Conjecture \ref{Final conjecture}
